Computer Science House Constitution

### 2016-01-25 articles.tex
Fixing blatant grammatical typo
Fixes typo noticed by @jeid64 in #13

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
\\*\\*
Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing. This may be appealed to the Executive Board in order to pursue a different outcome.
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

\asection{Types of Voting}
\asubsection{Alternative Vote}
\asubsubsection{Method of Vote}
Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.

Candidates are elected outright if they gain more than half the votes as first preferences. If not, the candidate who lost (the one with least first preferences) is eliminated and their votes move to the second preference marked on the ballot papers. This process continues until one candidate has half of the votes and is elected.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote} 
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote. A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time. At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period. The Vote Counters then tally the results.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period} 
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. Votes are kept anonymous. The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote. A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place. If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.

>>>>

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
\\*\\*
Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing. This may be appealed to the Executive Board in order to pursue a different outcome.
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject to any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

\asection{Types of Voting}
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote} 
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote. A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time. At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period. The Vote Counters then tally the results.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period} 
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. Votes are kept anonymous. The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote. A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place. If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.
